### 2015-08-30 463assignment/463assignment_takei.tex
added to do points

\section*{\normalsize{Abstract}}

@@

\subsection*{Intro to olfactory receptors}

@@

OR genes also have an important implications in the evolution of different species.
There are two major classes of OR genes: class I and class II genes, or ``fish-like'' and ``mammalian-like'' genes respectively, as the different classes of genes belong to their respective species (ref original paper or Nei and Niimura 2005).
The study by Niimura and Nei (2005) showed that the diversity of the OR gene family in fishes was greater than that of the mammalian OR gene family, even though the number of OR genes in a single family were less in fishes.
Furthermore, they showed that amphibians have retained the diversity of the gene family as the fishes, while also having the large repertoire of OR genes in one family as in the mammals, signifying the fact that the CNV was likely due to the adaptation process from being aquatic to terrestial (Nei and niimura, 2005).
As both pseudogenization and CNV are evidence of genomic drift (ref Nei et al, 2007).

\subsection*{Intro to copy number variations}

@@

@@

@@

@@

\subsection*{What am I going to do???}

>>>>

\section*{Abstract}

@@

\subsection*{Olfactory Receptors}

@@

OR genes also have an important implications in the evolution of different species.
There are two major classes of OR genes: class I and class II genes, or ``fish-like'' and ``mammalian-like'' genes respectively, as the different classes of genes are found mainly in their respective species (ref original paper or Nei and Niimura 2005).
The study by Niimura and Nei (2005) showed that the diversity of the OR gene families in fishes was greater than that of the mammalian OR gene family, even though the number of OR genes in a single family were less in fishes.
Furthermore, they showed that amphibians have retained the diversity of the gene families as the fishes, while also having the large repertoire of OR genes in one family as in the mammals, signifying the fact that the CNV was likely due to the adaptation process from being aquatic to terrestial (Nei and niimura, 2005).

Another study by Liman (2006) showed that pseudogenization and CNVs of the ORs coincided with the trichromatic vision in primates.
Although this is an evidence of how trichromacy in primates became more important than the ORs for their survival, better understanding of the ligands of the ORs is crucial to support this theory.

%As both pseudogenization and CNV are evidence of genomic drift, it is of great interest for researchers to understand the evolutionary process of ORs by studying the OR CNV (ref Nei et al, 2007).

\subsection*{Next Generation Sequencing and Copy Number Variations}

@@

studies have been relatively small -- possibly due to Sequencing limitations.
talk about 1000 genome project -- provides greater sample size to work with
limitations of sequencing CNVs -- highly variable, hard to sequence/annotate??

@@

relate this to obesity and eating disorder

@@

evolution and healthier eating

@@

gather sample to identify the OR genes that could be important -- get samples with known smelling disorder/condition
sequence the samples and identify the CNV difference and target those genes for further work
check 1000 genome database for any correlation and/or evidence of evolution
